---
title: "How to use the pagglomR package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{demo}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This brief vignette demonstrates how the `pagglomR` package can be used to 
calculate scheme agglomeration impacts. 

Suppose we have a national roads scheme and, as part of the project appraisal 
process, a transport model has been developed. We have AM, Inter-peak and PM
peak models with Cars and HGVs defined as separate user classes. For each 
future year model, we have a Do Minimum (without scheme) and a Do Something 
(with scheme) scenario.

Using the strategic transport modelling software (e.g. VISUM, SATURN) we can 
output text files and/or csv files listing the generalised cost and number of 
modelled trips for each origin destination pair. This can be output for each 
scenario and for each time period, user class and journey purpose depending on 
the structure of the transport model. 

For each scenario, mode of travel (i.e. highway and/or public transport) and 
each forecast year, a weighted average generalised cost is required across each 
time period, journey purpose, and user class. This can be calculated as follows:

$$
\begin{aligned}
GC_{i, j} ^ {S, m, f} &= \frac{\sum_{p} \ GC_{i, j} ^ {S, m, p, f} \ T_{i, j} ^ {S, m, p, f}} {\sum_{p} \ T_{i, j} ^ {S, m, p, f}}
\end{aligned}
$$
where:

* $GC_{i, j} ^ {S, m, f}$ is the weighted average generalised costs of travel, 
between zones $i$ and area $j$, for each mode $m$ in the scenario $S$ and the 
forecast year $f$.

* $GC_{i, j} ^ {S, m, p, f}$ is the generalised cost of trips from zone $i$ to 
zone $j$, scenario $S$, mode $m$ and purpose $p$ in the forecast year $f$.

* $T_{i, j} ^ {S, m, p, f}$ is thenumber of trips from zone $i$ to zone $j$ in 
the scenario $S$ by mode $m$ and purpose $p$ in the forecast year $f$.

In order for the generalised cost files to be read into `R` and used in the 
`pagglomR` package, they should be in comma separated value (csv) format with 
the column headings `o_zone`, `d_zone` and `gen_cost`.

In the case of outputs from a multi-modal transport model, seperate generalised 
cost skim matrices should be produced for private and public transport modes 
e.g. road and rail. These matrices should then be summed for each forecast year 
and scenario for input into the effective density calculations outlined below.

Weighted average generalised cost matrices should produced for commuting and 
business purposes only as productivity benefits are only associated with these
journey purposes. Also, the modelled time periods to be included should be based
on AM peak, Inter-Peak and PM peak. Off peak periods should not be considered as
these periods are not active from the perspective of commuting and business use.

A number of sample generalised cost outputs are included with the `pagglomR` 
package for the purposes of this example and for reference.

```{r setup}
library(pagglomR)

dm_2024
```

A sample jobs file is also included with with the `pagglomR` package.

```{r}
head(jobs)
```

In this example we have 3 modelled years - 2024, 2039 & 2054. We have 2 
scenarios for each modelled year - "Do Minimum" and "Do Something". For each 
year we first calculate the effective densities for each sector for both 
scenarios using the generalised costs from the transport model and the jobs 
data. This is undertaken using the `calc_eff_dens()` function which applies 
the following formula:

$$
\begin{aligned}
d_i^{S, k, f} &= \sum_{j} \sum_{m} \frac{E_j^{S,f}}{(GC_{i,j}^{S,m,f})a^k}
\end{aligned}
$$
where:

* $d_i^{S, k, f}$ is the effective density $d$ of origin area $i$ sector $k$ in 
each scenario $S$ for forecast year $f$.

* $E_j^{S,f}$ is is the total number of jobs for all sectors in zone $j$ for each 
scenario $S$ for forecast year $f$. Note that the number of jobs will be the 
same in both the Without Scheme (i.e. Do Minimum) and With Scheme (i.e. Do
Something) scenarios.

* $GC_{i,j}^{S,m,f}$ is is the average generalised cost of travel from area $i$
to area $j$ in the scenario $S$ for mode $m$,

* $a^k$ is the is the decay parameter for each sector $k$. This is held constant 
irrespective of the forecast year.

* $k$ is the is the aggregated industrial sector i.e. Manufacturing, 
Construction, Wholesale & Retail, Transport, Information & Communications 
Technology and Financial and Business Services.

```{r}
# 2024
eff_dens_dm_2024 <- calc_eff_dens(dm_2024, jobs, 2024)
eff_dens_ds_2024 <- calc_eff_dens(ds_2024, jobs, 2024)

# 2039
eff_dens_dm_2039 <- calc_eff_dens(dm_2039, jobs, 2039)
eff_dens_ds_2039 <- calc_eff_dens(ds_2039, jobs, 2039)

# 2054
eff_dens_dm_2054 <- calc_eff_dens(dm_2054, jobs, 2054)
eff_dens_ds_2054 <- calc_eff_dens(ds_2054, jobs, 2054)
```

We can then calculate the productivity impacts for each modelled year using the
effective density calculations for the "Do Minimum" and "Do Something" scenarios
and the jobs data. The productivity impacts are calculated by applying the
following formula:

$$
\begin{aligned}
WEI_i^{k, f} &= \left[ \left( \frac{d_i^{DS, k, f}}{d_i^{DM, k, f}} \right)^{\rho^k} - 1\right] GVA_i^{DM,k,f} E_i^{DM,k,f}
\end{aligned}
$$
where:

* $WEI_i^{k, f}$ is the sectoral agglomeration impacts for each zone $i$ and 
sector $k$ in each forecast year $f$.

* $d_i^{DS, k, f}$ and $d_i^{DM, k, f}$ are the effective densities of origin 
zone $i$ and sector $k$ in the "Do Something" and the "Do Minimum" scenarios 
respectively. This will vary depending on the forecast year (f)3 due to the 
change in the Generalised Cost of Travel over time associated with higher levels
of traffic demand.

* $\rho^k$ is the elasticity of productivity with respect to effective density 
for sector $k$. This is held constant irrespective of the forecast year.

* $GVA_i^{DM,k,f}$ is the Gross Value Added (GVA) per worker of each area $i$ 
and sector $k$ in the Do Minimum scenario. This will vary depending on the 
forecast year $f$ in line with expected productivity growth.

* $E_i^{DM,k,f}$ is the total number of jobs in sector $k$ in origin area $i$ in
the Do Minimum scenario. This will vary depending on the forecast year $f$ in 
line with projected job growth.

The `calc_prod_impacts()` function sums the above sectoral agglomeration imapcts
into an overall productivty impact in Euro (€, in 201X prices).

```{r}
# 2024
prod_2024 <- calc_prod_impacts(eff_dens_dm_2024, eff_dens_ds_2024, jobs)

# 2039
prod_2039 <- calc_prod_impacts(eff_dens_dm_2039, eff_dens_ds_2039, jobs)

# 2054
prod_2054 <- calc_prod_impacts(eff_dens_dm_2054, eff_dens_ds_2054, jobs)
```

The `discounted_prod()` function reads in the producitivty benefits calculated for 
each modelled year and interpolates values for years in between the modelled 
years. 

It also calculates nominal productivity benefits per annum by applying GVA 
growth based on the rates in Table 4 of PAG Unit 6.11. Discounted benefits are 
then calculated by applying the test discount rate to the nominal benefits. This 
is undertaken for the 30 year appraisal period plus a 30 year residual value 
period.

```{r}
# discounted table of benefits
discounted_benefits <- discounted_prod(appraisal_year = 2020,
                                       prod_2024, 
                                       prod_2039,
                                       prod_2054)

discounted_benefits
```

The discounted benefits can be summarised into a total present value benefit 
over the 30 year appraisal period, and a seperate total for the residual value 
period using the `prod_summary()` function.

```{r}
summary_benefits <- prod_summary(discounted_benefits)

summary_benefits
```

The total productivity impacts in present value terms can be calculated using:

```{r}
sum(summary_benefits$pv_benefits)
```

This can be added to the transport user benefits to produce an updated benefit
cost ratio (BCR) as part of a sensivity test around the central case in the 
scheme appraisal.
